Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-10 WRITEUP/ms.tex
minor fig size change

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16-28-PVE-highncut.png}
\caption{
Same as \Fig{alpha16-28}, but only the denser substructures of the main disk of \flower are included
(i.e., MCs here are identified with the highest $n_{\rm cut}$).
\label{fig:alpha16-28-highncut}}
\end{figure*}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) 
compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
(magenta circles, green stars, blue dots, and black triangles) and empirical relations 
established based on \obs of the Milky Way.
Star symbols are color-coded by increasing $n_{\rm cut}$.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
% \citep{Lombardi10a}.
\label{fig:MR}}
\end{figure*}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-alphavir-highncut.png}
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/ss16-28-PVE-highncut.png}
\caption{
Same as \Fig{alpha16-28}, but only the denser substructures of the main disk of \flower are included
(i.e., MCs here are identified with the highest $n_{\rm cut}$).
\label{fig:alpha16-28-highncut}}
\end{figure}

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) 
compared to observational data of molecular clouds in the Milky Way associated with massive \SF 
(magenta circles, green stars, blue dots, and black triangles) and empirical relations 
established based on \obs of the Milky Way.
Star symbols are color-coded by increasing $n_{\rm cut}$.
Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}.
Red line shows the threshold for massive \SF reported by \citet{Kauffmann10b}.
% \citep{Lombardi10a}.
\label{fig:MR}}
\end{figure*}
